---
title: "P8105_hw1 building block"
output: github_document
---
Author: Minghui Wang, mw3743<br>
Date: 2024-09-12

The purpose of this file is to complete the questions in [howework 1](https://p8105.com/homework_1.html).

# Problem 1
## 1.1 Describe the `penguins` dataset
Write a short description of the penguins dataset using inline R code.<br> 
```{r}
# Input data
data("penguins", package = "palmerpenguins")

# Acquire the data in this dataset, including names / values of important variables
summary(penguins)

# Acquire the size of the dataset (using nrow and ncol)
nrow(penguins)
ncol(penguins)

# Acquire the mean flipper length
mean(penguins$flipper_length_mm, na.rm = TRUE)
```
**Description of the `penguins` dataset**
- The penguins dataset consists of 344 rows and 8 columns. It contains data from penguins of three species, which are Adelie, Chinstrap, and Gentoo. Some important variables in the data are species, island(Biscoe, Dream, or Torgersen), bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year. The size of the penguins dataset is 344 rows and 8 columns. Additionally, the mean flipper length in the dataset is 200.92 mm.

## 1.2 Make scatterplot 

- Make a scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x); color points using the `species` variable:
```{r, warning=FALSE}
library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color =  species )) + geom_point()+
         labs(title = "Scatterplot of Flipper Length vs Bill Length", 
            x = "Bill Length (mm)", 
            y = "Flipper Length (mm)")
```

- Export first scatterplot to project directory
```{r, warning=FALSE}
ggsave("scatterplot_flipper_vs_bill.png", height = 4, width = 6)
```

# Problem 2
## Create data frame
```{r results='hide'}

```
## Take mean of each variable
```{r results='hide'}

```