---
title: "P8105_hw1 building block"
output: github_document
---
Author: Minghui Wang, mw3743<br>
Date: 2024-09-12

The purpose of this file is to complete the questions in [howework 1](https://p8105.com/homework_1.html).

# Problem 1
## Describe the `penguins` dataset
### Use of inline R code
```{r}
# Input data
data("penguins", package = "palmerpenguins")

# Acquire the data in this dataset, including names / values of important variables
summary(penguins)

# Acquire the size of the dataset (using nrow and ncol)
nrow(penguins)
ncol(penguins)

# Acquire the mean flipper length
mean(penguins$flipper_length_mm, na.rm = TRUE)
```
### Description of the `penguins` dataset
The penguins dataset consists of 344 rows and 8 columns. It contains data from penguins of three species, which are Adelie, Chinstrap, and Gentoo. Some important variables in the data are species, island(Biscoe, Dream, or Torgersen), bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year. The size of the penguins dataset is 344 rows and 8 columns. Additionally, the mean flipper length in the dataset is 200.92 mm.

## Make scatterplot 
```{r}

```
# Problem 2
## Create data frame
```{r results='hide'}

```
## Take mean of each variable
```{r results='hide'}

```