---
title: "P8105_hw1 building block"
output: github_document
---
Author: Minghui Wang, mw3743<br>
Date: 2024-09-12

The purpose of this file is to complete the questions in [howework 1](https://p8105.com/homework_1.html).

# Problem 1

## 1.1 Describe the `penguins` dataset
### 1.1.1 Explore the `penguins` dataset
```{r}

# Input data
data("penguins", package = "palmerpenguins")

# Acquire the data in this dataset, including names / values of important variables
summary(penguins)

# Acquire the size of the dataset (using nrow and ncol)
nrow(penguins)
ncol(penguins)

# Acquire the mean flipper length
mean(penguins$flipper_length_mm, na.rm = TRUE)

```

### 1.1.2 Description of the `penguins` dataset
The penguins dataset consists of 344 rows and 8 columns. It contains data from penguins of three species, which are Adelie, Chinstrap, and Gentoo. Some important variables in the data are species, island(Biscoe, Dream, or Torgersen), bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year. The size of the penguins dataset is 344 rows and 8 columns. Additionally, the mean flipper length in the dataset is 200.92 mm.

## 1.2 Make scatterplot 

### 1.2.1 ggplot 2
Make a scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x); color points using the `species` variable:
```{r, warning=FALSE}
#load package
library(ggplot2)

#make scatterplot
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color =  species )) + geom_point()+
         labs(title = "Scatterplot of Flipper Length vs Bill Length", 
            x = "Bill Length (mm)", 
            y = "Flipper Length (mm)")

```

### 1.2.2 Export scatterplot 
Export first scatterplot to project directory
```{r, warning=FALSE}

ggsave("scatterplot_flipper_vs_bill.png", height = 4, width = 6)

```

# Problem 2

## 2.1 Create data frame
The data frame should comprise of:
- a random sample of size 10 from a standard Normal distribution
- a logical vector indicating whether elements of the sample are greater than 0
- a character vector of length 10
- a factor vector of length 10, with 3 different factor “levels”

```{r, results = 'hide', message = FALSE, warning = FALSE}
library(tidyverse)
```

```{r}

# define data frame containing required variables
q2_df = tibble(
  norm_samp = rnorm(10, mean = 0),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("China", "USA", "Germany", "France", "Brazil","Japan", "Canada", "Australia", "India", "South Africa"),
  vec_factor =factor(c("Moderate", "Light","Moderate", "Vigorous", "Light","Moderate", "Vigorous" ,"Light","Moderate", "Vigorous"))
)
# display the data frame
q2_df

```

## 2.2 Take mean of each variable

### 2.2.1 Pull and calculate mean
```{r results='hide'}
mean(q2_df %>% pull(norm_samp))      
mean(q2_df %>% pull(norm_samp_pos))  
mean(q2_df %>% pull(vec_char))       
mean(q2_df%>% pull(vec_factor))  
```
**Findings**: The numeric variable(norm_samp) and logical variable(norm_samp_pos) can be used to take the mean while character vector and factor vector cannot and return NA.

### 2.2.2 Convert variables types into numeric
```{r,results='hide'}

as.numeric(q2_df %>% pull(norm_samp))
as.numeric(q2_df %>% pull(norm_samp_pos))
as.numeric(q2_df %>% pull(vec_char))
as.numeric(q2_df %>% pull(vec_factor))

```
**Findings**: I noticed a warning, "NAs introduced by coercion," when attempting to convert a character vector to numeric using `as.numeric()`. However, this warning does not appear when converting other variable types. The reason is that character vectors are not numerical data and cannot be coerced into numeric form. As a result, `NA` values are generated during the conversion with `as.numeric()`. This helps explain why taking the mean of a character vector fails.